\begin{document}
\section{Appendix}

\subsection{Common Aims}
    \begin{itemize}
      \item Explore characteristics of big data in a distributed setting where data is generated in continuous streams and need combination of real time and batch processing 
    
      \item Assess feasibility of the Smart Parking System to handle computations on Big Data (where the processing and data storage can be done in hierarchy of computing and communication resources). 
    
      \item To identify the functional and non-functional requirements of Smart Parking and the needs for using machine learning in this context. 
    
      \item To determine where machine learning can be implemented that can meet performance requirements (can be done at gateway level, fog or cloud level). 
    \end{itemize}


\subsection{Personal Research Aims}
    \begin{itemize}
        \item What kind of architecture/framework would this system use to achieve the functional and non-functional requirements?  
        
        \item What are the existing tools available to us, which we can use to build a Real Time Embedded System?
        
        \item What kind of data can be analysed, and the operations needed to be performed (Machine Learning)? 
        
        \item What will be the Machine Learning Tasks/Algorithms to be executed in the system? 
        
        \item What are tools available within the framework to do ML and how do they differ from those commonly used in wider academic/industry applications? 
    \end{itemize}
\end{document}