\begin{document}
\begin{thebibliography}{}
\bibitem{b1}“State of the IoT 2018: Number of IoT devices now at 7B – Market accelerating,” 08-Aug-2018. [Online].
Available: https://iot-analytics.com/state-of-the-iot-update-q1-q2-2018-number-of-iot-devices-now-7b/.
\bibitem{b1} D. Widyastuti and Irwansyah, “Benefits And Challenges Of Cloud Computing Technology Adoption In Small
And Medium Enterprises (SMEs),” Benefits And Challenges Of Cloud Computing Technology Adoption In Small
And Medium Enterprises (SMEs) | Atlantis Press, 01-Feb-2018. [Online]. Available: https://www.atlantispress.com/proceedings/bcm-17/25892201. [Accessed: 02-May-2020].
\bibitem{b1} X. Wang, Y. Han, V. C. Leung, D. Niyato, X. Yan, and X. Chen, “Convergence of Edge Computing and Deep
Learning: A Comprehensive Survey,” IEEE Communications Surveys & Tutorials, pp. 1–1, 2020.
\bibitem{b1}S. Nguyen, Z. Salcic, and X. Zhang, “Big Data Processing in Fog - Smart Parking Case Study,” 2018 IEEE Intl Conf
on Parallel & Distributed Processing with Applications, Ubiquitous Computing & Communications, Big Data &
Cloud Computing, Social Computing & Networking, Sustainable Computing & Communications
(ISPA/IUCC/BDCloud/SocialCom/SustainCom), 2018.
\bibitem{b1} Alexandru, Adriana & Alexandru, Cristina & Coardos, Dora & Tudora, Eleonora.. Big data: Concepts,
Technologies and Applications in the Public Sector. International Journal of Computer, Electrical, Automation,
Control and Information Engineering. (2016)
Commented [ZS5]: Define first
12
\bibitem{b1} W.I.R.E.D.B. Lab, “The Sensor-Based Economy,” Wired, 10-Apr-2017. [Online]. Available:
https://www.wired.com/brandlab/2017/01/sensor-based-economy/. [Accessed: 02-May-2020].
\bibitem{b1}M.S. Mahdavinejad, M. Rezvan, M. Barekatain, P. Adibi, P. Barnaghi, and A. P. Sheth, “Machine learning for
internet of things data analysis: a survey,” Digital Communications and Networks, 12-Oct-2017. [Online].
Available: https://www.sciencedirect.com/science/article/pii/S235286481730247X. [Accessed: 02-May2020].
\bibitem{b1}Y.G, “The 7 Steps of Machine Learning,” Medium, 07-Sep-2017. [Online]. Available:
https://towardsdatascience.com/the-7-steps-of-machine-learning-2877d7e5548e. [Accessed: 02-May-2020].
\bibitem{b1} E.I. Vlahogianni, K. Kepaptsoglou, V. Tsetsos, and M. G. Karlaftis, “A Real-Time Parking Prediction System for
Smart Cities,” Journal of Intelligent Transportation Systems, vol. 20, no. 2, pp. 192–204, 2015.
\bibitem{b1}Y.Atif, S.Kharrazi, D. Jianguo, and S. F. Andler, “Internet of Things data analytics for parking availability
prediction and guidance,” Transactions on Emerging Telecommunications Technologies, Aug. 2020 C. Badii, P.
Nesi, and I.Paoli, “Predicting Available Parking Slots on Critical and Regular Services by Exploiting a Range of
Open Data,” IEEE Access, vol. 6, pp. 44059–44071, 2018.
\bibitem{b1} A. Origlia, S. D. Martino, and Y. Attanasio, “On-Line Filtering of On-Street Parking Data to Improve Availability
Predictions,” 2019 6th International Conference on Models and Technologies for Intelligent Transportation
Systems (MT-ITS), 2019.
\bibitem{b1} W. Shao, Y. Zhang, B. Guo, K. Qin, J. Chan, and F. D. Salim, “Parking Availability Prediction with Long Short
Term Memory Model,” Green, Pervasive, and Cloud Computing Lecture Notes in Computer Science, pp. 124–
137, 2019.
\bibitem{b1} F. M. Awan, Y. Saleem, R. Minerva, and N. Crespi, “A Comparative Analysis of Machine/Deep Learning
Models for Parking Space Availability Prediction,” Sensors, vol. 20, no. 1, p. 322, Jun. 2020.
\bibitem{b1} D. Fumo, “A Gentle Introduction To Neural Networks Series - Part 1,” Medium, 22-Oct-2017. [Online].
Available: https://towardsdatascience.com/a-gentle-introduction-to-neural-networks-series-part-1-
2b90b87795bc. [Accessed: 02-May-2020].
\bibitem{b1} N. Mustafa, “A Systemic IoT-Fog-Cloud Architecture for Big-Data Analytics and Cyber Security Systems: A
Review of Fog Computing,” University of New South Wales-Canberra @ ADFA.[Online]. Available:
https://arxiv.org/pdf/1906.01055.pdf. [Accessed: 02-May-2020].
\bibitem{b1} L. L. Dhirani, T. Newe, E. Lewis, and S. Nizamani, “Cloud computing and Internet of Things fusion: Cost
issues,” 2017 Eleventh International Conference on Sensing Technology (ICST), 2017.
\bibitem{b1} “Spark Overview,” Overview - Spark 2.4.5 Documentation. [Online]. Available:
https://spark.apache.org/docs/latest/. [Accessed: 02-May-2020].
\bibitem{b1} N. Maleki, M. Loni, M. Daneshtalab, M. Conti, and H. Fotouhi, “SoFA: A Spark-oriented Fog
Architecture,” IECON 2019 - 45th Annual Conference of the IEEE Industrial Electronics Society, 2019.
\bibitem{b1} M. Huang, D. Wu, C. Yu, Z. Fang, M. Interlandi, T. Condie, and J. Cong, “Programming and Runtime Support to
Blaze FPGA Accelerator Deployment at Datacenter Scale” 2016. In Proceedings of the Seventh ACM
Symposium on Cloud Computing (SoCC ’16). Association for Computing Machinery, New York, NY, USA, 2017,
456–469.
\bibitem{b1} “Spark Structured Streaming,” Databricks, 11-Dec-2019. [Online]. Available:
https://databricks.com/blog/2016/07/28/structured-streaming-in-apache-spark.html. [Accessed: 03-May2020].
\bibitem{b1} Apache Spark™ - Unified Analytics Engine for Big Data. (n.d.). Retrieved from https://spark.apache.org/
\bibitem{b1} Analytics Zoo. (n.d.). Retrieved from https://software.intel.com/content/www/us/en/develop/topics/ai/analyticszoo.html
\bibitem{b1} BigDL. (n.d.). Retrieved from https://software.intel.com/content/www/us/en/develop/tools/frameworks/bigdl.html
\bibitem{b1} [z] Yanxu Zheng, S. Rajasegarar and C. Leckie, "Parking availability prediction for sensor-enabled car parks in smart cities," 2015 IEEE Tenth International Conference on Intelligent Sensors, Sensor Networks and Information Processing (ISSNIP), Singapore, 2015, pp. 1-6, doi: 10.1109/ISSNIP.2015.7106902. 
\end{thebibliography}
\end{document}